Supplementary material

### 2022-01-26 submission/supplement.rmd
add treatment interaction scenarios

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: false
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  - \newcommand\given[1][]{\:#1\vert\:}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

@@

```{r discriminationSampleSize, cache=FALSE, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 17,000", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r discriminationAuc, cache=FALSE, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.85 and sample size of 4,250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r calibrationSampleSize, cache=FALSE, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 17,000", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r calibrationAuc, cache=FALSE, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.85 and sample size of 4,250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

@@

>>>>

---
title: "Supplementary material"
output:
    bookdown::pdf_document2: default
geometry: margin=1.0in
toc: true
font-size: 12pt
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  - \newcommand\given[1][]{\:#1\vert\:}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
csl: jce.csl
---

@@

```{r discriminationSampleSize, cache=TRUE, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 17,000", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r discriminationAuc, cache=TRUE, echo=FALSE, fig.cap="Discrimination for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.85 and sample size of 4,250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/discrimination_moderate_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r calibrationSampleSize, cache=TRUE, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.75 and sample size of 17,000", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

```{r calibrationAuc, cache=TRUE, echo=FALSE, fig.cap="Calibration for benefit of the considered methods across 500 replications calculated in a simulated sample of size 500,000. True prediction AUC of 0.85 and sample size of 4,250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/calibration_moderate_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

@@

# Treatment interactions

Here we present the root mean squared error of the considered methods
when true interactions of the covariates with treatment are
assumed. We ran our analyses on a limited set of scenarios. More
specifically, true prediction AUC was set to 0.75 and sample size was
set to 4,250. The simulation scenarios included 4 weak interactions
($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=0.82$), 4 strong interactions
($\text{OR}_{t_x=1} / \text{OR}_{t_x=0}=0.61$), and 2 weak and 2
strong interactions.

```{r rmseInteraction, cache=FALSE, echo=FALSE, fig.cap="RMSE of the considered methods across 500 replcations calculated in a simulated sample of size 500,000. AUC is 0.85 rather than in Figure \\ref{fig:rmseHighBase}.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_interaction.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
